ms_5

### 2020-04-02 ms_4.Rmd
moved drug overdose csv but graph still not showing

# This first data set is the new data set for the week. This data provides
# state-specific numbers from the CDC regarding the number of drug overdose
# deaths per state as well as the predicted numbers for drug overdose deaths. I
# am super excited to plot this graph onto a map and look at how the worst
# affected states change over time.

>>>>

# This first data set provides
# state-specific numbers from the CDC regarding the number of drug overdose
# deaths per state as well as the predicted numbers for drug overdose deaths. I
# am super excited to plot this graph onto a map and look at how the worst
# affected states change over time.

### 2020-04-02 ms_5.Rmd
moved drug overdose csv but graph still not showing

*Reading in drug overdose data was copy pasted from last week
```{r, echo = FALSE}

# This first data set is the new data set from last week. This data provides
# state-specific numbers from the CDC regarding the number of drug overdose
# deaths per state as well as the predicted numbers for drug overdose deaths. I
# am super excited to plot this graph onto a map and look at how the worst
# affected states change over time.

drugoverdosedeaths<- read.csv(
  "VSRR_Provisional_Drug_Overdose_Death_Counts.csv") %>%
  clean_names() %>%
  select("state", "year", "month", "indicator", 
         "data_value", "state_name", "predicted_value") %>%

@@

@@

>>>>

```{r}

# This first data set provides
# state-specific numbers from the CDC regarding the number of drug overdose
# deaths per state as well as the predicted numbers for drug overdose deaths. I
# am super excited to plot this graph onto a map and look at how the worst
# affected states change over time.

drugoverdosedeaths<- read.csv(
  "ms_6/VSRR_Provisional_Drug_Overdose_Death_Counts.csv") %>%
  clean_names() %>%
  select("state", "year", "month", "indicator", 
         "data_value", "state_name", "predicted_value") %>%

@@

```{r}
# This data tracks the spending over a course of five years of a series of
# drugs. I want to compare the spending levels of the different kinds of drugs
# by categorizing them based on their use. Perhaps, we will find a correlation
# between spending and drug type for opioid deaths.

drugspending<-read.csv("Medicare Part B Drug Spending YTD 2017.csv", skip = 3) %>%
clean_names() %>%
  select("drug_description", "brand_name", "generic_name","x2013_total_spending", "x2013_total_dosage_units", "x2014_total_spending", "x2014_total_dosage_units", 
  "x2015_total_spending", "x2015_total_dosage_units", "x2016_total_spending", 
  "x2016_total_dosage_units", "x2017_total_spending", "x2017_total_dosage_units",
  "change_in_average_spending_per_dosage_unit_2016_2017", "annual_growth_rate_in_average_spending_per_dosage_unit_2013_2017")
```

```{r}

# This data set displays the number of deaths caused by opioids per county in NY
# over a course of 15 years.

deathbycounty_ny<- 
  read.csv("Vital_Statistics__Opioid-Related_Deaths_by_County__Beginning_2003.csv") %>%
  clean_names()

# Using data commons, I isolated drug spending in NY on some of the worst drugs
# of addiction and treatment drugs such as Methadone, Buprenorphine, and Naloxone.

drugspending_ny<- read.csv("New York Drug Spending.csv") %>%
  clean_names() %>%
  rename( Buprenorphine = "new_york_drug_dea_9064") %>%
  rename( Cocaine = "new_york_drug_dea_9041l") %>%
  rename( Methadone = "new_york_drug_dea_9250b") %>%
  rename( Naloxone = "new_york_drug_dea_9411")

# I want to compare the drug spending in NY (a state that has a lot of opioid
# data with the country that has the worst opioid addiction rates, West
# Virginia)

drugspending_wv<- read.csv("West Virginia Drug Spending.csv") %>%
clean_names() %>%
  rename( Buprenorphine = "west_virginia_drug_dea_9064") %>%
  rename( Cocaine = "west_virginia_drug_dea_9041l") %>%
  rename( Methadone = "west_virginia_drug_dea_9250b") %>%
  rename( Naloxone = "west_virginia_drug_dea_9411")

```

@@

```{r}
library(shiny)
library(tidyverse)
library(gt)
library(dplyr)
library(ggplot2)
library(lubridate)

### Read in Data
drugoverdosedeaths<- read.csv("ms_6/VSRR_Provisional_Drug_Overdose_Death_Counts.csv")

drugoverdosedeaths <- drugoverdosedeaths %>%
    clean_names() %>%
    select("state", "year", "month", "indicator", 
           "data_value", "state_name", "predicted_value") %>%
    filter(str_detect(indicator, "Drug Overdose Deaths")) %>%
    group_by("state_name") %>%
    mutate(time = paste(month, year, sep = " "))
drugoverdosedeaths$time<- as.factor(drugoverdosedeaths$time)
drugoverdosedeaths$time<- fct_relevel(drugoverdosedeaths$time, "January 2015", "February 2015", 
                                "March 2015", "April 2015", 
                                "May 2015", "June 2015", "July 2015", "August 2015", "September 2015", 
                                "October 2015", "November 2015", "December 2015", 
                                "January 2016", "February 2016", "March 2016", 
                                "April 2016", 
                                "May 2016", "June 2016", "July 2016", "August 2016", "September 2016", 
                                "October 2016", "November 2016", "December 2016", 
                                "January 2017", "February 2017", 
                                "March 2017", "April 2017", "May 2017", 
                                "June 2017", "July 2017", "August 2017", "September 2017", 
                                "October 2017", "November 2017", "December 2017", 
                                "January 2018", "February 2018", 
                                "March 2018", "April 2018", 
                                "May 2018", "June 2018", "July 2018", "August 2018", 
                                "September 2018", "October 2018", "November 2018", "December 2018",
                                "January 2019", "February 2019", 
                                "March 2019", "April 2019", 
                                "May 2019", "June 2019", "July 2019") 
drugoverdosedeaths$data_value <-as.numeric(drugoverdosedeaths$data_value)

        ggplot(drugoverdosedeaths, aes(x= reorder(state_name,-data_value), y= data_value)) +
            geom_col() +
            facet_wrap(~time)
            labs(title = "Drug Overdose Deaths by State Over Time", 
                 x = "State", 
                 y = "Drug Overdose Deaths") +

            theme(axis.text.x = element_text(angle = 45, hjust = 1))

```
